---
title: "Estimating causal `policyFX` with `clusteredinterference`"
author: "Brian G. Barkley"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{estimate-policyFX}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

First, load the `clusteredinterference` package 

```{r}
library(clusteredinterference)
```

Now load a quick data example that's included in the package

```{r}
data("toy_data") 
```

## Estimation

Estimation is implemented with the `policyFX()` function:

```{r} 
suppressWarnings(RNGversion("3.5.0")) ## For backwards compatibility 
set.seed(1113)
causal_fx <- policyFX(
  data = toy_data,
  formula = Outcome | Treatment ~ Age + Distance + (1 | Cluster_ID) | Cluster_ID,
  alphas = c(.3, .5), 
  k_samps = 1
)

```

The `policyFX()` function outputs a `"policyFX"` object, which works well with a few methods, including:

```{r}
summary(causal_fx)
```

### Necessary arguments

#### `data` 

A `data.frame`. At present, `tibble`s are coerced back to standard `data.frame`s. I also recommend against using `factor`s in the columns.

#### `alphas`

A numeric vector of probabilities corresponding the the policies of interest. Each must be between 0 and 1. 

#### `k_samps`

The user must specify the number of sum-sampled vectors for estimating the counterfactual probabilities (nuisance parameters). It is recommended to choose `k_samps <=5`. To avoid the sub-sampling approximation and use all possible vectors, set `k_samps=0`.

#### `formula`

The formula may be the trickiest, and it has plenty of information. It provides:

```{r, eval = FALSE}
outcome | treatment ~ predictors and random intercept | clustering specification
```

Note that the middle section is passed to `glmer()` to fit the mixed effects model, so this is how to specify the modeling formula.

```{r, eval = FALSE}
Treatment ~ Age + Distance + (1 | Cluster_ID)
```

See below for the model output.

### Formal arguments with defaults

#### `verbose = FALSE`

#### `root_options = NULL`

This is for `rootSolve::multiroot()` used in the point estimation procedure. E.g., this will be passed in:

```{r, eval = FALSE}
root_options = list(atol = 1e-7) 
```

#### `nAGQ=2`

This is for `lme4::glmer()`. The default in `glmer()` is `nAGQ=1`, which indicates a Laplace approximation to the log-likelihood. Instead, in this package the default is `nAGQ=2`, which indicates that `n=2` Adaptive Gaussian Quadrature points will be used. This is slightly slower but is a more accurate calculation. In limited testing, it seems that `nAGQ=2` was almost as accurate as higher values, so 2 was chosen as the default. See their documentation for more details.

#### `return_matrices = FALSE`
  
If `TRUE`, this will return the "bread" and "meat" matrices in the variance calculations. The default is `FALSE` as these matrices can be quite large.


### Dots tricks

In the event you're only interested in a subset of contrasts, you can pass a customized grid into the function.

```{r} 
my_grid <- makeTargetGrid(alphas = (3:8)/20, small_grid = TRUE) 
head(my_grid)
```

This can be particularly useful for plotting, as you can "turn off" the variance estimates 

```{r}
my_grid$estVar <- FALSE
```

This is available through the dots argument. Note that when supplying a custom `target_grid`, it's not necessary to specify the `alphas` argument, as that is taken directly from `target_grid`.

```{r}
causal_fx2 <- policyFX(
  data = toy_data,
  formula = Outcome | Treatment ~ Age + Distance + (1 | Cluster_ID) | Cluster_ID,
  # alphas = c(.3, .5), 
  target_grid = my_grid,
  k_samps = 5,
  verbose = FALSE,
  root_options = list(atol=1e-4)
)

print(causal_fx, nrows = 9)
```

### Plotting 

The tidy dataframe `estimates` can be easily used for plotting:

```{r, fig.width = 6, fig.height = 5}
plotdat <- causal_fx2$estimates[causal_fx2$estimates$estimand_type=="mu",]
plot(x = plotdat$alpha1, y = plotdat$estimate, main = "Estimated Population Means")
```

### Treatment model

As mentioned above, the treatment model is specified via the `formula` argument. For example, compare:

```{r}
# Returns the specified formula, coerced to a Formula object
causal_fx$formula
# causal_fx$model is a glmerMod S4 object
causal_fx$model@call
lme4::getME(causal_fx$model, c("beta", "theta"))
```



