---
title: "Illustration of Estimator"
author: "Brian G. Barkley"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

First, load this package 

```{r}
library(clusteredinterference)
```

Now load a quick data example

```{r}
library(inferference)
data("vaccinesim", package = "inferference") 
head(vaccinesim)

```

## Estimation

Estimation is implemented with one function:



```{r} 
type_C <- policyFX(
  data = vaccinesim[1:300,],
  formula = Y | A ~ X1 + X2 + (1|group) | group,
  alphas = c(.3, .5), 
  k_samps = 1,
  verbose = FALSE
)

```

### Necessary arguments

#### `data` 

A `data.frame`. At present, `tibble`s are coerced back to standard `data.frame`s. I also recommend against using `factor`s in the columns.

#### `alphas`

#### `formula`

The formula is the trickiest, and it has plenty of information. It provides:

```{r, eval = FALSE}
Y | A ~ X1 + X2 + (1|group) | group
outcome | treatment ~ predictors and random intercept | clustering specification
```

Note that the middle section is passed to `glmer()` to fit the mixed effects model, so this is how to specify the modeling formula!

```{r, eval = FALSE}
A ~ X1 + X2 + (1|group)
```
### Recommended arguments

#### `k_samps`

### Formal arguments with defaults

#### `verbose = FALSE`

#### `root_options = NULL`

This is for `rootSolve::multiroot()` used in the point estimation procedure. E.g., this will be passed in:

```{r, eval = FALSE}
root_options = list(atol = 1e-7) 
```

#### `nAGQ=2`

This is for `lme4::glmer()`. The default in `glmer()` is `nAGQ=1`, which indicates a Laplace approximation to the log-likelihood. Instead, in this package the default is `nAGQ=2`, which indicates that `n=2` Adaptive Gaussian Quadrature points will be used. This is slightly slower but is a more accurate calculation. In limited testing, it seems that `nAGQ=2` was almost as accurate as higher values, so 2 was chosen as the default. See their documentation for more details.

#### `return_matrices = FALSE`
  
If TRUE, this will return the "bread" and "meat" matrices in the variance calculations.




### Dots tricks

In the event you're only interested in a subset of contrasts, you can pass a customized grid into the function.

```{r} 
my_grid <- makeTargetGrid(alphas = c(0.3, 0.5), small_grid = TRUE)
my_grid <- my_grid[is.na(my_grid$trt), ]
my_grid
```

This is available through the dots argument. Note that when supplying a custom `target_grid`, it's not necessary to specify the `alphas` argument, as that is taken directly from `target_grid`.

```{r}
type_C <- policyFX(
  data = vaccinesim[1:300,],
  formula = Y | A ~ X1 + X2 + (1|group) | group,
  # alphas = c(.3, .5), 
  target_grid = my_grid,
  k_samps = 1,
  verbose = TRUE
)

```


